### 2012-06-19 inst/examples/value_of_information.Rmd

``` {r sethiplots, cache=FALSE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

@@

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3]
  })
})
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r profits, fig.cap="the distribution of profits by scenario"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

>>>>

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

@@

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario", dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````
